An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-27 paper/4.xpg.tex
add subsection names

\section{Tupling and lazy updates: xpg}
\subsection{pg}

Another solution for saving intermediate states is tupling. If $put$ and $get$ are evaluated simultaneously, it is potential to reduce the number of recomputed $get$s. The following function, $pg$, accepts the pair of a source and a view as the input to produce a new pair that contains the actual result of the corresponding minBiGUL program.

@@

\subsection{cpg}

@@

\subsection{kpg}

@@

\subsection{xpg}
The most important thing when using $kpg$ to evaluate a composition $bx_1 \circ bx_2$ is keeping the dropped parts from the source in a function that is used to produce new source instead of using more recursive call. This is reflected in the first call $\kpginline{bx_1}$ and the last application in $\kpginline{bx_1 \circ bx_2}$. The second call $\kpginline{bx_2}$ just play an syntactic role while it requires many parameters. We can completely reduce this number to 2, including one for the source and one for the view as in a $pg$ call. This idea is realized by function $xpg$ as follows:

>>>>

\section{Tupling and lazy updates: xpg}
\subsection{Tupling: pg}
s
Another solution for saving intermediate states is tupling. If $put$ and $get$ are evaluated simultaneously, it is potential to reduce the number of recomputed $get$s. The following function, $pg$, accepts the pair of a source and a view as the input to produce a new pair that contains the actual result of the corresponding minBiGUL program.

@@

\subsection{Lazy update: cpg}

@@

\subsection{Lazy computation: kpg}

@@

\subsection{Combination of pg and kpg: xpg}
The most important thing when using $kpg$ to evaluate a composition $bx_1 \circ bx_2$ is keeping the dropped parts from the source in a function that is used to produce new source instead of using more recursive call. This is reflected in the first call $\kpginline{bx_1}$ and the last application in $\kpginline{bx_1 \circ bx_2}$. The second call $\kpginline{bx_2}$ just play an syntactic role while it requires many parameters. We can completely reduce this number to 2, including one for the source and one for the view as in a $pg$ call. This idea is realized by function $xpg$ as follows:
